Semantic High-definition Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-10-23 cvpr2018.tex
revision

\section{Method}
Figure \ref{fig:archs} illustrate the overall method.

@@

\section{Method}
To generate high-resolution photo-realistic images from text embeddings, we propose a simple and effective multi-level Generative Adversarial Network architecture. Our model mainly consists of the following key-components,

\textbf{Advantages} Figure \ref{fig:archs-compare} illustrates the architecture difference between widely-used cascade strategy \cite{han2017stackgan,denton2015deep} and our strategy. Compared with it,

\subsection{Overview}
In this paper, we use the following notations. Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively. for simplicity we assume the image is all square. The generator is denoted $G: \mathcal{R}^{Z}: \times \mathcal{R}^{T}\rightarrow\mathcal{R}^{I}$, the image discriminator $D_i: \mathcal{R}^{I}\rightarrow\{0, 1\}$, and the matching-aware discriminator $D_m: \mathcal{R}^{I}: \times \mathcal{R}^{T}\rightarrow\{0, 1\}$.

As is shown in Fig\ref{game}, In the generator $G$, we first sample a random vector $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$, then text embedding vector $\psi{t}$ is obtained by applying an per-trained text encoder on the image description $t$, in this paper, we use the char-rnn based text encoder provided in \cite{reed2016generative}.

\textbf{Variational text encoding: } Following the work of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the origin al $\Psi(t)$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$. This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $\psi_t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to $G$ that totally ignores the noise, resulting to results lacking diversity.

Conditioned on $c$ and the random vector $z$, a synthetic image $\hat{x}$ is generated as $\hat{x}\leftarrow G(c,z)$, it is simply a feed forward pass of the generator. Our generator consists of stacks of residual blocks, bilinear sampling layer is used to up-sample the feature maps.

The discriminator $D$ in our model mainly consists of two branches: matching-aware pair discrimination branch $D_{pair}$, and image discrimination branch $D_{img}$, both branches share the same  image encoder.

@@

 \subsection{Scalable Deeply Supervised}
 \textbf{Multi-level side output:} instead of only predicting the high resolution in the final output, our model is designed to predict multi-level images of gradually increasing dimension (e.g., 256$\times$256 as the final output with 64$\times$64 and 128$\times$128 being the side output) as the side outputs. In principle, the lower-resolution side output is forced to learn the rough structure (e.g., object sketch, color information and background) of the images, the subsequent higher-resolution path is used to add more details to the images. The lower-level side output works by regularizing the lower-level image feature. Since the model is trained in an end-to-end fashion, we can observe more consistent information exhibited in both lower and higher-resolution outputs than stackGan\cite{han2017stackgan}. This type of side output is also proven useful because it allows short path between image supervision information to the hidden feature maps, which could potentially helps training.

\subsection{Generator Loss}
The generator's goal is to generator image that match the input text embedding and looks as real as possible. So the loss function for our model mainly consists of two parts, namely, matching aware loss and one image loss.  
Given a set of chosen input pair $(x, \psi_t)$, the generator is optimizing the following function
 \begin{equation}
 \label{genloss}
 \begin{split}
 \mathcal{L}_G = & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{sent}( G(z, c_t),  \psi_t) ) ] + \\
				  & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{img}( G(z, c_t) ) ) ] + \\
                  & D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) 		   
 \end{split}
 \end{equation}
 where $c_t$ is the variational conditional vector generated from $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$. To make the network differentiable, in practice, we adopted the re-parametric trick\cite{vae}, where $c_t$ is actually computed as $\mu(\psi_t)+\Sigma(\psi_t)\odot \epsilon$, where $\epsilon\in \mathcal{R}^{T}$ is draw from a normal Gaussian distribution.

\subsection{Functional Loss of Discriminator}
 Our goal is to generate images that not only look as realistic as real images, but also matching the given text description.
 Therefore, the discriminator must handle errors of the following two categories: real image with mismatch conditional text information, fake image with real text. In order to achieve this, the previously proposed matching aware discriminator is explicitly trained with three pair configurations, namely: real image with right text as positive training sample, and the aforementioned two sources of error pairs as negative training samples.

>>>>

\textbf{Advantages} Figure \ref{fig:archs-compare} illustrates the architecture difference between widely-used cascade strategy \cite{han2017stackgan,denton2015deep} and our strategy. Compared with it, 
\\

\section{Method}
Figure \ref{fig:archs} illustrate the overall method.
%To generate high-resolution photo-realistic images from text embeddings, we propose a simple and effective Hierarchically-nested Generative Adversarial Network.
Our approach is to train both generator and discriminator conditioned on sentence embedding vectors. We leverage functional loss for discriminator and hierarchically nested side outputs as hierarchical supervision for both generator and discriminator to achieve our goal of generating photo-realistic images from text descriptions.  In general, the generator takes text embedding and random noise vector as input and synthesis images at different scales (e.g, $64\times64$, $128\times128$, $256\times256$). The discriminator, on the other hand, is trying to judge the pair of synthesized images and the corresponding text embedding as fake pairs as well as differentiating the real images from the fake images. $G$ and $D$ are optimized alternatively until converges.

\subsection{Overview}
In this paper, we use the following notations. Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively. Please note that, $G$ has multiple branches and generates multiple images of different sizes and for each image size, we have a distinct $D$. For simplicity, we only describe one image size.

The generator is denoted $G: \mathcal{R}^{Z}: \times \mathcal{R}^{T}\rightarrow\mathcal{R}^{I}$, the image discriminator $D_{img}: \mathcal{R}^{I}\rightarrow\{0, 1\}$, and the matching-aware pair discriminator $D_{pair}: \mathcal{R}^{I}: \times \mathcal{R}^{T}\rightarrow\{0, 1\}$.

\textbf{Variational text embedding: } Following the work of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $\Psi_t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$. This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $\psi_t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}. In addition, using this kind of text embedding makes the input pure stochastic, making it more difficult for the generator to over fit the training data.

@@

\subsection{Scalable Deeply Supervised}
Instead of only predicting the high resolution in the final output, our model is designed to predict multi-level images of gradually increasing dimension (e.g., 256$\times$256 as the final output with 64$\times$64 and 128$\times$128 being the side output).

In principle, the lower-resolution side output is forced to learn the rough structure (e.g., object sketch, color information and background) of the images, the subsequent higher-resolution path is used to add more details to the images.

The lower-level side output works by regularizing the lower-level image feature. Since the model is trained in an end-to-end fashion, we can observe more consistent information exhibited in both lower and higher-resolution outputs than stackGan\cite{han2017stackgan}. This type of side output is also proven useful because it allows short path between image supervision information to the hidden feature maps, which could potentially helps training.

\subsection{Generator Loss}
As is shown in Fig\ref{game}, In the generator $G$, we first sample a random vector $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$, then text embedding vector $\psi_{t}$ is obtained by applying an per-trained text encoder on the image description $t$, in this paper, we use the char-rnn based text encoder provided in \cite{reed2016generative}.

Conditioned on variational text embedding $c$ and the random vector $z$, a synthetic image $\hat{x}$ is generated as $\hat{x}\leftarrow G(c,z)$, it is simply a feed forward pass of the generator. The generator $G$ consists of stacks of residual blocks, bilinear sampling layer is used to up-sample the feature maps.

The generator's goal is to generator image that match the input text embedding and looks as real as possible. So the loss function for our model mainly consists of two parts, namely, matching aware loss and one image loss.

Given a set of chosen input pair $(x, \psi_t)$, the generator is optimizing the following function
 \begin{equation}
 \label{genloss}
 \begin{split}
 \mathcal{L}_G = & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{sent}( G(z, c_t),  \psi_t) ) ] + \\
				  & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{img}( G(z, c_t) ) ) ] + \\
                  & D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) 		   
 \end{split}
 \end{equation}
 where $c_t$ is the variational conditional vector generated from $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$. To make the network differentiable, in practice, we adopted the re-parametric trick\cite{vae}, where $c_t$ is actually computed as $\mu(\psi_t)+\Sigma(\psi_t)\odot \epsilon$, where $\epsilon\in \mathcal{R}^{T}$ is draw from a normal Gaussian distribution.

\subsection{Functional Loss of Discriminator}

As is shown in Figure. \ref{overview}, the discriminator $D$ in our model mainly consists of two branches: matching-aware pair discrimination branch $D_{pair}$, and image discrimination branch $D_{img}$, both branches share the same  image encoder.

@@

 Our goal is to generate images that not only look as realistic as real images, but also matching the given text description.
 Therefore, the discriminator must handle errors of the following two categories: real image with mismatch conditional text information, fake image with real text. In order to achieve this, the previously proposed matching aware discriminator is explicitly trained with three pair configurations, namely: real image with right text as positive training sample, and the aforementioned two sources of error pairs as negative training samples.
